{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-24 documents/background.tex
More discussion

@@

@@

\begin{fquote}[Wait][ \cite{treatyelectromagnetic}]
HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
IEEE C95.1-2005 safety standard [n.b. chapter 4.3, Table 9, subsection e. peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis. 
\end{fquote}

@@

Dykeman \cite{Vibrational2009} perform an all-atom molecular dynamics simulation of ISRU of phage M13, albeit without a heat bath to accurately represent damping. An interesting result is that despite the broadband nature of the pulse, \char`~80\% of the pulse energy couples into only 5 modes, starting at approx. 20 GHz. The binding energy is implied to be too high to explain the experimental results.

>>>>

Much of the work in this paper was concerned with this paper

@@

On the other hand, the maximum amplitude of oscillation is only expected to be on the order of 50 picometers.

@@

\begin{fquote}[NATO Research Task Group 189][ \cite{treatyelectromagnetic}]
HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
IEEE C95.1-2005 safety standard [n.b. chapter 4.3, Table 9, subsection e. peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis. 
\end{fquote}

@@

Dykeman \cite{Vibrational2009} perform an all-atom molecular dynamics simulation of ISRU of phage M13, albeit without a heat bath to accurately represent damping. An interesting result is that despite the broadband nature of the pulse, \ntilde80\% of the pulse energy couples into only 5 modes, starting at approx. 20 GHz. The binding energy is implied to be too high to explain the experimental results.

### 2021-01-24 documents/brillouin_pulse_math.tex
I find a bug in prop_num_optimize
More discussion

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
This is based on a lagrange multiplier technique\cite{Methods1989} and variational 
calculus\footnotetext{} .

@@

Note the ni in the complex conjugate!

@@

Using an energy constraint, appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.

>>>>

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
This is based on a lagrange multiplier technique and variational 
calculus\cite{Methods1989} \footnotetext{Based on personal communication with Professor Costas Sarris}.

@@

Note the ni specifically in the complex conjugate!

@@

Using an energy constraint as above appears to tend towards a square step function or a sharp impulse, perhaps as a result of Pontryagin's maximum principle\cite{Optimum1964}.

However, a maximum absolute value constraint produces fantastic results.

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
	\caption{Second.}
\end{figure}

 Believed to be FFT window artifacts. Increasing the window size with the same sample rate caused CG convergence to stall.

### 2021-01-24 documents/charge.tex
Progress
progress
why's fdtd broken?
More discussion

%!TeX root = charge
\documentclass[paper.tex]{subfiles}
\usepackage{parselines}

@@

@@

\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge on the virion changes}

@@

Viral capsids self-assemble; it is energetically favorable to.

@@

\footnotetext{
For an impermeable virus like the even-numbered T's, the inside salt concentration is set by the incubation solution's value of nb. Anderson et al. (1953) found in the case of T6, upon rapid dilution with distilled water, for example, that incubation nb values on the order of 1.5 M were required for osmotic shock. From Eq. 2, and n0 \approx 3 M, it follows that nin $\approx 0.62 M$ and hence n++ n- \approx 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \approx 3 M.
}
https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555

@@

\section{Hello World}
\label{sec:hello}
\hyperref[sec:hello]{See section.}

>>>>

%!TeX root = charge
\documentclass[paper.tex]{subfiles}
%\usepackage{parselines}

@@

Induced polarization

Nuclocapsid

The adsorption of metal ions onto the surface of the genome,

effective

\subsection{Birefringence }

\subsection{Electrorotation }

\subsection{Poisson-Boltzmann }

@@

\footnote{Influenza also has several other fascinating electrostatic properties. First, the net charge on the virion changes on a decade-by-decade basis \cite{Dynamics2010}. }

@@

@@

\footnotetext{
For an impermeable virus like the even-numbered T's, the inside salt concentration is set by the incubation solution's value of nb. Anderson et al. (1953) found in the case of T6, upon rapid dilution with distilled water, for example, that incubation nb values on the order of 1.5 M were required for osmotic shock. From Eq. 2, and n0 \ntilde 3 M, it follows that nin $\approx 0.62 M$ and hence n++ n- \ntilde 4.2 M, which because of the Donnan equilibrium is indeed significantly larger than 2nb \ntilde 3 M.
}
%https://www-sciencedirect-com.ezproxy.library.yorku.ca/science/article/pii/S0006349503744555

@@

Bosch \cite{Studies1985}
